---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/coatless/uiucdata.svg?branch=master)](https://travis-ci.org/coatless/uiucdata)[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/uiucdata)](http://www.r-pkg.org/pkg/uiucdata) [![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/uiucdata)](https://cran.r-project.org/package=uiucdata)

# `uiucdata`

The goal of `uiucdata` is to provide data sets available at the
[University of Illinois at Urbana-Champaign (UIUC)](http://illinois.edu/) 
to a diverse group of individuals with a low barrier for entry.

## Installation

You can install `uiucdata` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("coatless/uiucdata")
```

## Example

There are two ways to access the data contained within this package. 

The first is to load the package itself and type the name of a data set.
This approach takes advantage of _R_'s lazy loading mechansim, which avoids
loading the data until it is used in _R_ session. For details on 
how lazy loading works, please see [Section 1.17: Lazy Loading](https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Lazy-loading)
of the [R Internals](https://cran.r-project.org/doc/manuals/r-release/R-ints.html)
manual.

```{r use-data-package, eval = FALSE}
# Load the `uiucdata` package
library("uiucdata")

# See the first 10 observations of the `fall_enrolled_ranking` dataset
head(fall_enrolled_ranking)

# View the help documentation for `fall_enrolled_ranking`
?fall_enrolled_ranking
```

The second approach is to use the `data()` command to load data on the 
fly without and type the name of a data set.

```{r use-data-call, eval = FALSE}
# Loading `fall_enrolled_ranking` without a `library(ucidata)` call
data("fall_enrolled_ranking", package = "uiucdata")

# See the first 10 observations of the `fall_enrolled_ranking` dataset
head(fall_enrolled_ranking)

# View the help documentation for `fall_enrolled_ranking`
?fall_enrolled_ranking
```


## Included Data Sets

The following data sets are included in the `ucidata` package:

- [Division of Management Information](http://www.dmi.illinois.edu/)
    - [Student Enrollment by Curriculum and Class Level](http://www.dmi.illinois.edu/stuenr/#class)
- [Freedom of Information Data Sets](https://www.uillinois.edu/cms/One.aspx?portalId=1324&pageId=171041)
    - Grade Distribution Data
- [Center for Innovation in Teaching and Learning (CITL)](http://citl.illinois.edu/)
    - Teachers Ranked as Excellent (Data courtesy of Wade-Fagen, see the [project repo for more details](https://github.com/wadefagen/Teachers-Ranked-As-Excellent-UIUC))

## Build Scripts

Want to see how each data set was imported? 
Check out the [`data-raw`](https://github.com/coatless/uiucdata/tree/master/data-raw) folder!

## Submodules

This repository uses submodules as a way to store data. This allows for us
to have the repositories contents as the final data product. As a result, 
we avoid increase the size of the repository since the raw data is now tracked
in a separate repository. For more details, please see GitHub's [Working with Submodules ](https://github.com/blog/2104-working-with-submodules) post.


### Example submodule inclusion statement

```bash
# Add Excellent Teacher Data in data-raw
git submodule add https://github.com/wadefagen/Teachers-Ranked-As-Excellent-UIUC data-raw/excellent-teachers
```

**NB** This repository is made by an employee of the University of Illinois at
Urbana-Champaign who is not the author of this data package.

----

Raw grade data

```bash
git submodule add https://github.com/coatless/uiucgradedata data-raw/grade-dist
```

## Coming Soon (TM)

- [Freedom of Information Data Sets](https://www.uillinois.edu/cms/One.aspx?portalId=1324&pageId=171041)
    - Graybook and Non-graybook Financials
    - Crime Statistics
